HyperLogLog: Exponentially Bad in Adversarial Settings

### 2022-01-31 docs/HLL_exp_bad/main.tex
redo tables

\begin{table*}[tb!]
\small\centering
\caption{Attack results for a classic HLL implementation, averaged over 50 iterations.}
\medskip
     \makebox[\linewidth]{
\begin{tabular}{| m{11em} | m{3.4em} | m{4.8em} | m{4.1em} | m{4.1em} | m{4.1em} | m{4em} |}
    \hline
    \textbf{Scenario} &  \multicolumn{2}{c|}{S1} & \multicolumn{2}{c|}{S2} & \multicolumn{2}{c|}{S4} \\ \hline
    %\textbf{HLL initially empty?} & yes & yes & yes & no & yes & no \\ \hline
    \textbf{Original Card. Est.} & 0 & 0 &  0 & 1,001 & 0 & 1,007  \\ \hline
    \textbf{\# Targeted buckets $B$} & 1 & 128 (= m/2) & 1 & - & 1 & - \\ \hline
      \textbf{\# Items added} & 4,132 & 523,791  & 4,106 & 524,851 & 4,106 & 857,150 \\ \hline
     \textbf{Final Card. Est.} & 1 & 177 & 1 & 1,025  & 1 &  1,007 \\ \hline
    \textbf{\# Resets} & 4,718 & 6,973 & - & - & - & - \\ \hline

\end{tabular}}
\label{table:tab1}
\end{table*}

\begin{table*}[tb!]
\small\centering
\caption{Attack results for a classic HLL implementation, averaged over 50 iterations, in the setting of~\cite{hllvuln}.}
\medskip
     \makebox[\linewidth]{
\begin{tabular}{| m{11em} | m{3.4em} | m{4.8em} | m{4.1em} | m{4.1em} | m{4.1em} | m{4em} |}
    \hline
    \textbf{Scenario} & \multicolumn{2}{c|}{S1} & \multicolumn{2}{c|}{S2} & \multicolumn{2}{c|}{S4} \\ \hline
    %\textbf{HLL initially empty?} & yes & yes & yes & no & yes & no \\ \hline
      \textbf{Original Card. Est.} & 0 & 0 & 0 & 1,001 & 0 & 1,003 \\ \hline
       \textbf{\# Targeted buckets $B$} & 1 & 128 (= m/2) & 1 & - & 1 & - \\ \hline
     \textbf{\# Items added} & 977 & 125,091 & 980 & 125,153 & 1,003 & 204,127 \\ \hline
    \textbf{Final Card. Est.} & 1 & 177 & 1 & 1,058  & 1 & 1,003 \\ \hline
    \textbf{\# Resets} & 1,148 & 1,655 & - & - & - & - \\ \hline

\end{tabular}}
\label{table:tab2}
\end{table*}

@@

\begin{table*}[tb!]
\small\centering
\caption{Attack results for HLL in Redis, averaged over 50 iterations.}
\medskip
     \makebox[\linewidth]{
\begin{tabular}{| m{11em} | m{4em} | m{4.2em} |}
    \hline
    \textbf{Scenario} &  \multicolumn{2}{c|}{S2} \\ \hline
    %\textbf{HLL initially empty?} & no & yes \\ \hline
    \textbf{Original Card. Est.} & 0 & 139,967 \\ \hline
     \textbf{$\epsilon$} &  0.5 & - \\ \hline
    \textbf{\# Items added} & 524,210 & 524,454\\ \hline
    \textbf{Final Card. Est.} & 13,185 & 139,967 \\ \hline
\end{tabular}}
\label{table:tab3}
\end{table*}
%\todo[inline]{Results from Redis or GBQ if we get them.}

>>>>

\begin{table*}[htp]
\caption{Attacks on empty sketches for a classic HLL implementation, averaged over 50 iterations.}
\begin{center}
\begin{tabular}{| l | >{\raggedleft\arraybackslash}p{5em} | >{\raggedleft\arraybackslash}p{5em} | >{\raggedleft\arraybackslash}p{5em} | >{\raggedleft\arraybackslash}p{5em} |}
	\hline
	\textbf{Scenario} &  \multicolumn{2}{c|}{S1} & S2 & S4  \\ \hline
	\textbf{Original Card. Est.} & 0 & 0 &  0  & 0   \\ \hline
	\textbf{\# Targeted buckets $B$} & 1 & 128 (= m/2) & 1 &  1 \\ \hline
	\textbf{\# Items added} & 4,132 & 523,791  & 4,106 & 4,106 \\ \hline
	\textbf{Final Card. Est.} & 1 & 177 & 1  & 1 \\ \hline
	\textbf{\# Resets} & 4,718 & 6,973 & - & - \\ \hline
\end{tabular}
\end{center}
\label{table:tab1}
\end{table*}%

%\begin{table*}[tb!]
%\small\centering
%\caption{Original Table: Attacks on empty sketches for a classic HLL implementation, averaged over 50 iterations.}
%\medskip
%     \makebox[\linewidth]{
%\begin{tabular}{| m{11em} | m{3.4em} | m{4.8em} | m{4.1em} | m{4.1em} | m{4.1em} | m{4em} |}
%    \hline
%    \textbf{Scenario} &  \multicolumn{2}{c|}{S1} & \multicolumn{2}{c|}{S2} & \multicolumn{2}{c|}{S4} \\ \hline
%    %\textbf{HLL initially empty?} & yes & yes & yes & no & yes & no \\ \hline
%    \textbf{Original Card. Est.} & 0 & 0 &  0 & 1,001 & 0 & 1,007  \\ \hline
%    \textbf{\# Targeted buckets $B$} & 1 & 128 (= m/2) & 1 & - & 1 & - \\ \hline
%      \textbf{\# Items added} & 4,132 & 523,791  & 4,106 & 524,851 & 4,106 & 857,150 \\ \hline
%     \textbf{Final Card. Est.} & 1 & 177 & 1 & 1,025  & 1 &  1,007 \\ \hline
%    \textbf{\# Resets} & 4,718 & 6,973 & - & - & - & - \\ \hline
%
%\end{tabular}}
%\label{table:tab1bis}
%\end{table*}

\begin{table*}[tb!]
\caption{Comparison of attack results in the S1 adversarial scenario, in the setting of~\cite{hllvuln}.}
\begin{center}
\begin{tabular}{| l | >{\raggedleft\arraybackslash}p{6.8em} | >{\raggedleft\arraybackslash}p{6.8em} | >{\raggedleft\arraybackslash}p{6.8em} |}
    \hline
    \textbf{Attack} & \multicolumn{2}{c|}{Ours} & ~\cite{hllvuln} \\ \hline
      \textbf{Original Card. Est.} & 0 & 0 & 0  \\ \hline
       \textbf{\# Targeted buckets $B$} & 1 & 128 (= m/2) & - \\ \hline
     \textbf{\# Items added} & 977 & 125,091 & 74,390 \\ \hline
    \textbf{Final Card. Est.} & 1 & 177 &  15,780 \\ \hline
    \textbf{\# Resets} & 1,148 & 1,655 & 3 \\ \hline

\end{tabular}
\end{center}
\label{table:tab2}
\end{table*}

\begin{figure*}[htp]
    \centering
    \begin{minipage}{0.45\textwidth}
        \centering
        \caption{Attack results as function of t in the S2 scenario.}
        \includegraphics[width=0.9\textwidth]{figures/graph_S2.pdf}
    \end{minipage}\hfill
    \begin{minipage}{0.45\textwidth}
        \centering
        \caption{Attack results as function of t in the S4 scenario.}
        \includegraphics[width=0.9\textwidth]{figures/graph_S4.pdf} % second figure itself
     \end{minipage}
    \label{fig:graphs}
\end{figure*}

%\begin{table*}[tb!]
%\small\centering
%\caption{Original Table: Attack results for a classic HLL implementation, averaged over 50 iterations, in the setting of~\cite{hllvuln}.}
%\medskip
%     \makebox[\linewidth]{
%\begin{tabular}{| m{11em} | m{3.4em} | m{4.8em} | m{4.1em} | m{4.1em} | m{4.1em} | m{4em} |}
%    \hline
%    \textbf{Scenario} & \multicolumn{2}{c|}{S1} & \multicolumn{2}{c|}{S2} & \multicolumn{2}{c|}{S4} \\ \hline
%    %\textbf{HLL initially empty?} & yes & yes & yes & no & yes & no \\ \hline
%      \textbf{Original Card. Est.} & 0 & 0 & 0 & 1,001 & 0 & 1,003 \\ \hline
%       \textbf{\# Targeted buckets $B$} & 1 & 128 (= m/2) & 1 & - & 1 & - \\ \hline
%     \textbf{\# Items added} & 977 & 125,091 & 980 & 125,153 & 1,003 & 204,127 \\ \hline
%    \textbf{Final Card. Est.} & 1 & 177 & 1 & 1,058  & 1 & 1,003 \\ \hline
%    \textbf{\# Resets} & 1,148 & 1,655 & - & - & - & - \\ \hline
%
%\end{tabular}}
%\label{table:tab2bis}
%\end{table*}

@@

\begin{table*}[tb!]
\begin{center}
\caption{Attack results for HLL in Redis, averaged over 50 iterations.}
\begin{tabular}{| m{11em} | m{4em} | m{4.2em} |}
    \hline
    \textbf{Scenario} &  \multicolumn{2}{c|}{S2} \\ \hline
    %\textbf{HLL initially empty?} & no & yes \\ \hline
    \textbf{Original Card. Est.} & 0 & 139,967 \\ \hline
     \textbf{$\epsilon$} &  0.5 & - \\ \hline
    \textbf{\# Items added} & 524,210 & 524,454\\ \hline
    \textbf{Final Card. Est.} & 13,185 & 139,967 \\ \hline
\end{tabular}
\end{center}
\label{table:tab3}
\end{table*}
%\todo[inline]{Results from Redis or GBQ if we get them.}
